\documentclass[11pt]{article}
\pagestyle{plain}
\usepackage[margin=1.0in,tmargin=0.75in,bmargin=0.75in]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\rfoot{\thepage}

\usepackage{amsmath,amssymb,graphicx,amsthm}
\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}

\usepackage[T1]{fontenc}
\usepackage{mathpazo} 
\setlength{\parindent}{0em}
\setlength{\parskip}{\baselineskip}

\DeclareMathOperator{\Span}{span}

\begin{document}
\title{Monty Hall Problem}
\section*{Algebra 2: Monty Hall Lab \hfill 9.3}
Name: \underline{\hspace{3in}} \hfill Date: \underline{\hspace{1in}}
\section*{Pre-Lab}
%http://www.randomservices.org/random/games/MontyHall.html
\subsection*{Background}
The Monty Hall Problem is based off of a classic game show called \textit{Let's Make a Deal}. In the show, the following steps happen:
\begin{enumerate}
\item The contestant selects one out of three  doors.  Only one of the doors has a prize behind it.
\item The host of the show selects a different door and opens it.
\item The host gives the contestant the option of switching from her original choice to the remaining closed door.
\item The door finally selected by the player is opened and she either wins or loses.
\end{enumerate}
The question is whether it is advantageous for the contestant to switch doors in step 3.

\subsection*{Critical Thinking Questions}
\begin{enumerate}
\item What possible outcomes are you able to get from this game?
\item What is the probability of each outcome?
\item Does the option to switch change the probability of winning the game?
\end{enumerate}

\section*{Experiment}
\begin{enumerate}
\item Find a partner.
\item Retrieve 3 cups and 3 tokens from the teacher.
\item Use the three cups to cover the three tokens, so that each cup is covering one token.
\item Have one group member play the part of the host, and another play the part of the contestant.
\item Have the contestant choose one cup.
\item Have the host reveal one unchosen cup that does not contain the prize.
\item Do \textbf{not} give the contestant the opportunity to switch.
\item Reveal what was under the contestant's cup.
\item Repeat this experiment 15 times total.
\item Record your results as you go in the space below:
\vspace{1in}
\item Repeat this experiment 15 times, except make the following changes:
\begin{enumerate}
\item On step 7 the contestant must choose the other unrevealed cup.
\end{enumerate}
\item Record your results as you go in the space below:
\vspace{1in}
\item Report your findings on the whiteboard.
\end{enumerate}
\section*{Post-lab}
\begin{enumerate}
\item Which strategy works best?
\item What is you hypothesis concerning the probabilities in the Monty Hall Problem?
\end{enumerate}
\vfill
How did you like this activity?
\par
0 \hfill 1 \hfill 2 \hfill 3 \hfill 4 \hfill 5\\
Not at all \hfill Best thing since sliced bread
\par
How can this activity be improved?
\end{document}